---
title: "Teaching Real Data"
author: "Thomas J. Pfaff"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The  **Teaching Real Data** project collects real-world data from sources such as scholarly journals and government agencies for use in statistics and data science courses. The data sets can be sorted by uses to make it easier for educators to identify data sets that fits their needs.

All data was listed as open source but if you would like it removed then send me an email at <tpfaff99@outlook.com>. Feedback and data suggestions are welcomed. This repository is licensed under GPL-2.

Visit my Substack [Briefed by Data][id] if you are interested in data, current events, or are curious.


***
***

```{r, echo=FALSE, warning=FALSE}
library(DT)
library(htmlwidgets) 

url <- "https://raw.githubusercontent.com/Thomas-Pfaff/TeachingRealDatasets/refs/heads/main/datasets.csv"
#url <- "datasets.csv"
data <- read.csv(url)

datatable(data,escape = FALSE, options = list(pageLength = 50))


```

[id]: https://briefedbydata.substack.com/